---
output: github_document
---

## An Extension of `googledrive` for the Reed College mLab

This is a quick extension to Jenny Bryan's `googledrive` package to allow for
grabbing data from Google Drive and returning it as an R object without 
saving the object to the user's local file system. This is meant to allow for 
several people to work with the same data without having to deal with
downloading files, changing filepaths, and `getwd()` fussiness.

This code can be used to load the package:

```{r, eval = FALSE}
library(devtools)
install_github("simonpcouch/googledriveplus")
library(googledriveplus)
```

The new function, `grab_data`, can be used like this:

```{r, display = FALSE, message = FALSE, warning = FALSE, include = FALSE}
library(devtools)
library(tidyverse)
load_all()
```

```{r, eval = FALSE}
grab_data(url = "https://drive.google.com/open?id=1JnkQddF8FmY0YsXZSWBanQNPjZ_LBIQUGi_s43vNDIQ",
          filetype = "Sheet")
```

```{r, message = FALSE, echo = FALSE}
grab_data(url = "https://drive.google.com/open?id=1JnkQddF8FmY0YsXZSWBanQNPjZ_LBIQUGi_s43vNDIQ",
          filetype = "Sheet")
```

There is *a lot* of `googledrive` (and other `tidyverse`) functionality lost when using this function---this should only be used for basic table loading.

Simon Couch
